Bioconductor has a repository and release schedule that differs from R.
It has a 'devel' and 'release' branch. The 'release' branch is emitted
twice per year (in April and October), to which bug fixes but not new features
are introduced. The whole system is a bit complicated. Basically the best way 
to install Bioconductor packages is with `BiocInstaller::biocLite()`.

BiocInstaller
=============
* Used to install and update Bioconductor, CRAN and some GitHub packages.
* Using `source("http://bioconductor.org/biocLite.R")` installs *and*
attaches the `BiocInstaller` package, with which you can install other
packages and check the version of Bioconductor in use.
* Since the `BiocInstaller` package is automatically attached, you don't need
to load it with `library()` or `require()`:


```{r ch1}
search()
source("http://bioconductor.org/biocLite.R")
search()
```

### biocLite
* Installs or updates Bioconductor, CRAN and some GitHub packages in a
Bioconductor release.

* It is a wrapper around `install.packages()`, but with the repository chosen
according to the version of Bioconductor in use, rather than to the version 
relevant at the time of the R release.

* It also nudges users to update packages.


**Usage**

```r
biocLite(pkgs=c("Biobase", "IRanges", "AnnotationDbi"),
         suppressUpdates=FALSE,
         suppressAutoUpdate=FALSE,
         siteRepos=character(),
         ask=TRUE, ...)
```

**Examples**

```{r foo, eval=FALSE}
# Installs default packages (Biobase, IRanges and AnnotationDbi) if not already
# installed, and updates previously installed packages.
biocLite()

# Install a CRAN package
biocLite("Hmisc")
# Install several Bioconductor packages
biocLite(c("limma", "edgeR"))
# Install a GitHub package
biocLite("kbroman/broman")
```

### Package Groups
Returns the names of packages associated with Bioconductor publications.

* `all_group()`: All Bioconductor packages;
* `biocases_group()`: Bioconductor Case Studies;
* `RBioinf_group()`: R Programming for Bioinformatics;
* `monograph_group()`: Bioinformatics and Computational Biology Solutions
Using R and Bioconductor;

**Examples**
```{r}
bioc_pkgs <- all_group()
str(bioc_pkgs)
bioc_pkgs[sample(length(bioc_pkgs), 10)]
```


### useDevel
Use the development version of Bioconductor. See `?BiocInstaller::usedevel` for
an excellent description.

